---
title: "The Incomparable Radio Network — In Numbers"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
#### Paackages ####
library(knitr)
library(rmdformats)
library(readr)
library(ggplot2)
library(magrittr)
library(dplyr)
library(lubridate)
library(tidyr)
library(DT)
library(formattable)
#library(svglite)
library(viridis)
library(stringr)
library(tadaatoolbox)

#### Global options ####
options(max.print = "75")
opts_chunk$set(echo    = FALSE,
	             cache   = FALSE,
               prompt  = FALSE,
               tidy    = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 75)

#### Data prep ####
incomparable_master      <- readRDS("data/incomparable_master.rds")
incomparable_master_wide <- readRDS("data/incomparable_master_wide.rds")

shows <- incomparable_master_wide %>% group_by(podcast) %>% tally() %>% arrange(desc(n)) %>% extract2("podcast")

incomparable_master_wide %<>%
  mutate(podcast = factor(podcast, levels = shows, ordered = T))

incomparable_master %<>%
  mutate(podcast = factor(podcast, levels = shows, ordered = T))

#### Plot presets ####
template_background <- element_rect(fill = "#fcfcfc", color = "#fcfcfc")

theme_background <- 
  theme(panel.background  = template_background,
        plot.background   = template_background,
        legend.background = template_background)

theme_breaks_x <-
  theme(panel.grid.major.x = element_line(size = .1, color = "black"),
        panel.grid.minor.x = element_line(size = .1, color = "black", linetype = "dotted"))
  
theme_breaks_y <-   
  theme(panel.grid.major.y = element_line(size = .1, color = "black"),
        panel.grid.minor.y = element_line(size = .1, color = "black", linetype = "dotted"))

```

[The Incomparable Radio Network](https://www.theincomparable.com/) spans **`r incomparable_master_wide$podcast %>% unique %>% length()`** shows (including the [Bonus Track](https://www.theincomparable.com/bonustrack/), but *not* including the [Greatest Hits feed](https://www.theincomparable.com/best)), **`r incomparable_master$person %>% unique %>% length()`** people and a combined runtime of over **`r incomparable_master_wide$duration %>% sum() %>% divide_by(60) %>% divide_by(24) %>% floor`** days.  
That's quite a lot.

# Overview

```{r master_shows}
incomparable_master_wide %>%
  group_by(podcast) %>%
  summarize(first_aired = min(date), last_aired = max(date), episodes = n(),
            primary_hosts = modus(host)) %>%
  arrange(desc(episodes)) %>%
  datatable(colnames = c("Show", "First Aired", "Last Aired", "# of Episodes", "Most Frequent Host(s)")) %>%
  formatDate(columns = c(2, 3))
```

# Shows

## Episodes Count (Total)

```{r shows_episodes}
incomparable_master %>%
  group_by(podcast) %>%
  summarize(n = length(unique(number))) %>%
  ggplot(aes(x = reorder(podcast, n), weight = n)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 1000, 50),
                     minor_breaks = seq(0, 1000, 10)) +
  labs(x = "Show", y = "# of Episodes") +
  theme_background +
  theme_breaks_x

incomparable_master %>%
  group_by(podcast) %>%
  summarize(n = length(unique(number))) %>%
  arrange(desc(n)) %>%
  datatable(colnames = c("Show", "# of Episodes"))
```

## Episodes per Year

### All Shows

```{r show_episodes_year_total}
incomparable_master_wide %>%
  group_by(podcast, year) %>%
  tally %>%
  ggplot(aes(x = year, weight = n, fill = podcast)) +
  geom_bar() +
  scale_y_continuous(breaks = seq(0, 1000, 100),
                     minor_breaks = seq(0, 1000, 25)) +
  scale_fill_viridis(discrete = T) +
  labs(x = "Year", y = "# of Episodes", fill = "Show") +
  theme_background +
  theme_breaks_y +
  theme(legend.key.size = unit(.5, "cm"))

incomparable_master_wide %>%
  group_by(year) %>%
  tally %>%
  arrange(desc(year)) %>%
  datatable(colnames = c("Year", "# of Episodes"))
```

### Per Show

```{r show_episodes_year, fig.height=8}
incomparable_master_wide %>%
  group_by(podcast, year) %>%
  summarize(n = length(unique(number))) %>%
  ggplot(aes(x = reorder(podcast, n), weight = n)) +
  geom_bar() +
  coord_flip() +
  facet_wrap(~year) +
  labs(x = "Show", y = "# of Episodes") +
  theme_background +
  theme_breaks_x

incomparable_master %>%
  group_by(podcast, year) %>%
  summarize(n = length(unique(number))) %>%
  arrange(desc(n)) %>%
  datatable(colnames = c("Show", "Year", "# of Episodes"))
```


# Runtimes

## Total Runtime by Show

```{r runtimes_total_show}
incomparable_master_wide %>%
  group_by(podcast) %>%
  summarize(episodes = length(unique(number)),
            hours    = round(sum(duration)/60, 2),
            days     = round(hours/60, 2)) %>%
  arrange(desc(episodes)) %>%
  {
    ggplot(., aes(x = reorder(podcast, hours), weight = hours)) +
    geom_bar() +
    coord_flip() +
    scale_y_continuous(breaks = seq(0, max(.$hours), 50)) +
    labs(x = "Show", y = "Hours") +
    theme_background +
    theme_breaks_x
  }

incomparable_master_wide %>%
  group_by(podcast) %>%
  summarize(episodes = length(unique(number)),
            hours    = round(sum(duration)/60, 2),
            days     = round(hours/60, 2)) %>%
  arrange(desc(episodes)) %>%
  datatable(colnames = c("Show", "# of Episodes", "Hours", "Days"))
```

## Average Runtime per Show

```{r runtimes_avg_show}
incomparable_master_wide %>% 
  group_by(podcast) %>%
  summarize(mean = mean(duration),
            upper = mean + confint_t(duration),
            lower = mean - confint_t(duration)) %>%
  ungroup %>%
  {
    ggplot(., aes(x = reorder(podcast, mean), y = mean)) +
    geom_errorbar(aes(y = mean, ymin = lower, ymax = upper), size = 1, width = .5) +
    geom_point(aes(y = mean), color = "red", size = 1) +
    geom_hline(aes(yintercept = mean(mean)), linetype = "dotted", color = "red") +
    coord_flip() + 
    scale_y_continuous(breaks = seq(0, max(.$upper) + 30, 15), 
                     minor_breaks = seq(0, max(.$upper) + 30, 5)) +
    expand_limits(y = 0) +
    labs(title = "Average Show Runtime\nwith CI and Global Average (red dotted)",
         x = "Show", y = "Average Runtime (mins) + 95% Confidence Interval") +
    theme_background +
    theme_breaks_x
  }

incomparable_master_wide %>%
  group_by(podcast) %>%
  summarize(minutes = round(mean(duration), 2),
            hours = round(mean(duration)/60, 2)) %>%
  arrange(desc(minutes)) %>%
  datatable(colnames = c("Show", "Minutes", "Hours"))
```

# People

## Appearances in Total

```{r people_appearances, fig.height=7}
incomparable_master %>%
  group_by(role, person) %>%
  tally %>% 
  arrange(person) %>%
  filter(person != "None") %>%
  group_by(person) %>%
  mutate(n_total = sum(n)) %>%
  ungroup() %>%
  filter(n > 2) %>% 
  {
    ggplot(., aes(x = reorder(person, n_total), weight = n, fill = role)) +
    geom_bar() +
    coord_flip() +
    scale_y_continuous(breaks = seq(0, max(.$n_total), 50),
                       minor_breaks = seq(0, max(.$n_total), 10)) +
    scale_fill_brewer(palette = "Set1") +
    labs(x = "Person (3 Appearances Minimum)", y = "Episodes", fill = "Role") +
    theme_background + 
    theme(legend.position = "top") +
    theme_breaks_x
  }

incomparable_master %>%
  group_by(role, person) %>%
  tally %>% 
  spread(role, n) %>%
  replace_na(list(guest = 0, host = 0)) %>%
  mutate(total = guest + host) %>%
  ungroup() %>%
  select(person, total, host, guest) %>%
  arrange(desc(total)) %>%
  datatable(colnames = c("Person", "Apperances Total", "As Host", "As Guest"))
```


