---
title: "The Incomparable Podcast — In Numbers"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
library(knitr)
library(rmdformats)
library(readr)
library(ggplot2)
library(magrittr)
library(dplyr)
library(lubridate)
library(tidyr)
library(DT)
library(formattable)
library(svglite)

## Global options
options(max.print = "75")
opts_chunk$set(echo    = FALSE,
	             cache   = FALSE,
               prompt  = FALSE,
               tidy    = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               dev = "svglite",
               fig.ext = ".svg")
opts_knit$set(width = 90)

incomparable <- readRDS("data/incomparable.rds")

incomparable %<>% 
  mutate(year = as.factor(year(date)),
         month = month(date, abbr = F, label = T),
         weekday = wday(date, label = T, abbr = F)) %>%
  select(number, date, year, month, weekday, duration, title, host, guest)
```

# Introduction

Well, [Jason Snell tweeted](https://twitter.com/jsnell/status/700864025949655040) a graph of The Incomparable runtimes.  
As a big fan of the podcast and an aspiring nerd, [I asked for the data, obviously](https://twitter.com/Jemus42/status/700864609083850753).  
I was happy to [receive his .numbers file](https://twitter.com/jsnell/status/700864809537970176), but unfortunately [it only contained two variables](https://twitter.com/Jemus42/status/700870531697004544) - the two needed for the plot.  
Jason replied [he could get more metadata if I liked](https://twitter.com/jsnell/status/700870702367318017) and since I **really really would like** that, I rushed to set up [this repository](https://github.com/jemus42/theincompaRable) and put on my data-pants.  
A short time after that, [Jason delivered magnificiently](https://twitter.com/jsnell/status/700882298795765761).  
And now my analysis begins.

# Episodes in General

```{r episodes_month}
incomparable %>%
  mutate(month = factor(month, levels = rev(levels(month)))) %>%
  ggplot(aes(x = month)) +
  geom_bar() +
  coord_flip() +
  facet_wrap(~year, ncol = 3)

incomparable %>%
  ggplot(aes(x = month)) +
  geom_bar() +
  facet_grid(year~.)
```

# Runtime

```{r runtime_}
ggplot(data = incomparable, aes(x = duration)) +
  geom_histogram() +
  labs(title = "The Incomparable Podcast\nShow Duration",
       x = "Duration (min)") +
  theme_bw()

ggplot(data = incomparable, aes(x = number, y = duration, colour = host)) +
  geom_point() +
  labs(title = "The Incomparable Podcast\nShow Duration",
       x = "Episode #", y = "Duration (min)") +
  theme_bw()
```

## Runtime by Host

```{r runtime_by_host}
ggplot(data = incomparable, aes(x = reorder(host, duration), y = duration)) +
  geom_boxplot() +
  coord_flip() +
  labs(title = "The Incomparable Podcast\nShow Duration by Primary Host",
       x = "Host (first listed)", y = "Duration (min)") +
  theme_bw()
```

## Runtime over Time

### Over Years

```{r runtime_years}
ggplot(data = incomparable, aes(x = year, y = duration)) +
  geom_boxplot()
```

### Over Years/Months

```{r runtime_yearmonth}
incomparable %>%
  mutate(month = factor(month, levels = rev(levels(month)))) %>%
  ggplot(aes(x = month, y = duration)) +
  geom_boxplot() +
  coord_flip() +
  facet_wrap(~year, ncol = 3)

```

### Weekdays

```{r runtime_wday}
ggplot(data = incomparable, aes(x = weekday, y = duration)) +
  geom_boxplot()
```

# Guests

```{r guests, fig.height=9}
incomparable %>%
  group_by(guest) %>%
  tally %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = reorder(guest, n), weight = n)) +
  geom_bar() +
  coord_flip() +
  labs(title = "The Incomparable Podcast\nGuest Appearances",
       x = "Guest", y = "# of Episodes") +
  theme_bw()

incomparable %>%
  group_by(guest) %>%
  summarize(n = n(), airtime_total = round(sum(duration), 2)) %>%
  arrange(desc(n)) %>%
  ungroup %>%
  mutate(perc_episodes = round((n/max(incomparable$number)) * 100, 2),
         perc_guests    = round((n/sum(n)) * 100, 2),
         perc_airtime = round(airtime_total/sum(incomparable$duration) * 100, 2)) %>%
  select(-airtime_total) %>%
  datatable(colnames = c("Guest", "Episodes", "Episode %", 
                         "% of Guests", "% of Guests by Airtime"))
```

# Acknowledgements

- Thanks to Jason for setting up the `stats.txt` files I parsed for the data.
- Thanks to [Juba](https://twitter.com/lapply) for the [RMarkdown template](https://github.com/juba/rmdformats)
