---
title: "The Incomparable: Missing Data"
author: "@Jemus42"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(dplyr)
library(DT)

incomparable_master      <- readRDS(file.path(Sys.getenv("PROJECT_HOME"), "data/incomparable_master.rds"))
incomparable_master_wide <- readRDS(file.path(Sys.getenv("PROJECT_HOME"), "data/incomparable_master_wide.rds"))
```

# List of episodes with missing metadata

This is page is a side effect of my attempts of compiling all of The Incomparable in data.  
During that process I noticed a few inconsistencies or oversights here and there, and so I thought I could compile them all in nice tables, so oversights can be fixed if so desired.  

All tables are **filterable** and **searchable**, to make things as easy as possible.

[Note on what I mean by "topic" and "category"](http://dump.jemu.name/MoVpb.png)

## Missing Category and Topic

Assuming that at least one of both should be set.

```{r missing_category_topic, echo=F}
incomparable_master_wide %>% 
  filter(topic == "Not provided" & category == "Not provided") %>%
  select(podcast, number, date, title, category, topic, host) %>%
  datatable(filter = "top", options = list(pageLength = 5)) %>%
  formatDate(columns = "date")
```

### Missing Category

This field doesn't make sense for all shows I guess, but at least for the main show it's quite useful.

```{r missing_category, echo=F}
incomparable_master_wide %>% 
  filter(category == "Not provided") %>%
  select(podcast, number, date, title, category, topic, host) %>%
  datatable(filter = "top", options = list(pageLength = 5)) %>%
  formatDate(columns = "date")
```

### Missing Topic

Yes, I know it's not strictly mandatory, but just in case it was an oversight.

```{r missing_topic, echo=F}
incomparable_master_wide %>% 
  filter(topic == "Not provided") %>%
  select(podcast, number, date, title, category, topic, host) %>%
  datatable(filter = "top", options = list(pageLength = 5)) %>%
  formatDate(columns = "date")
```


## Shows with only one person listed

Yes, some episodes only feature one person, like *Summer Superhero Spectacular: The Aftermath* (**Incomparable #255e**), but overall it's not the norm, and I'm pretty sure **Incomparable 255c** has more than one person talking in it, or I'm hearing voices.

As for the **Radio Theatre**:  
I don't know if all participants or only the writer should be listed, but since it's not my place to judge anyway, I'm including it in this table for now.


```{r missing_people, echo=F}
incomparable_master %>%
  group_by(podcast, number) %>%
  mutate(people_count = length(person)) %>%
  ungroup %>%
  filter(people_count <= 1) %>%
  select(podcast, number, date, title, role, person) %>%
  arrange(desc(date)) %>%
  datatable(filter = "top", options = list(pageLength = 10)) %>%
  formatDate(columns = "date")
```

# Related Documents

- [The main show](http://stats.jemu.name/theincomparable/results_incomparable.html)
- [All shows](http://stats.jemu.name/theincomparable/results_incomparable_master.html)
- [All shows, raw data](http://stats.jemu.name/theincomparable/incomparable_raw.html)
