---
title: "Relay.fm — In Numbers"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output:
  rmdformats::readthedown:
    highlight: kate
    self_contained: false
    fig_height: 5
    fig_width: 8
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
#### Paackages ####
library(knitr)
library(rmdformats)
library(readr)
library(ggplot2)
library(magrittr)
library(dplyr)
library(lubridate)
library(tidyr)
library(DT)
library(scales)
library(viridis)
library(stringr)
library(tadaatoolbox)
library(ggrepel)
library(plotly)

#### Global options ####
options(max.print = "75")
opts_chunk$set(echo    = FALSE,
	             cache   = FALSE,
               prompt  = FALSE,
               tidy    = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               fig.retina = 2)
opts_knit$set(width = 75)

#### Data prep ####
relay      <- readRDS(file.path(data_dir, "relay.rds")) %>% filter(year >= 2014)

shows <- relay %>% group_by(podcast) %>% tally() %>% arrange(desc(n)) %>% extract2("podcast")

relay %<>%
  mutate(podcast = factor(podcast, levels = shows, ordered = T))

#### Plot presets ####
template_background <- element_rect(fill = "#fcfcfc", color = "#fcfcfc")

theme_background <- 
  theme(panel.background  = template_background,
        plot.background   = template_background,
        legend.background = template_background,
        strip.background  = template_background)

theme_breaks_x <-
  theme(panel.grid.major.x = element_line(size = .1, color = "black"),
        panel.grid.minor.x = element_line(size = .1, color = "black", linetype = "dotted"))
  
theme_breaks_y <-   
  theme(panel.grid.major.y = element_line(size = .1, color = "black"),
        panel.grid.minor.y = element_line(size = .1, color = "black", linetype = "dotted"))

```

# Intro

After doing [The Incomparable](http://stats.jemu.name/theincomparable/results_incomparable_master.html), I had to go see what I could with [Relay.fm's](https://relay.fm) data as well, naturally.  
So this is the beginning of that. The source code is included in [the original repo](https://github.com/jemus42/theincompaRable), and, in case anyone asks:  
Yes, you can use these graphs for whatever. Maybe link back to me, that would be cool.

Please note that there's probably still stuff coming.

# Overview

```{r text_placeholders}
projection <- relay %>%
  group_by(podcast) %>%
  summarize(first_aired = min(date),
            last_aired = max(date),
            episodes = length(unique(number))) %>%
  mutate(lifetime_weeks = as.numeric(difftime(last_aired, first_aired, units = "weeks")),
         episodes_per_week = episodes / lifetime_weeks) %>%
  transmute(ep_yearly = episodes_per_week * 52) %>%
  summarize(sum(ep_yearly)) %>% 
  as.numeric() %>%
  round()

lastyear <- relay %>% filter(year == year(now())-1) %>% nrow()
thisyear <- relay %>% filter(year == year(now())) %>% nrow()
progress <- round(thisyear/projection * 100)
```


[Relay.fm](https://relay.fm/) spans **`r relay$podcast %>% unique %>% length()`** shows and a combined runtime of over **`r relay$duration %>% sum() %>% divide_by(60) %>% divide_by(24) %>% floor`** days spread across **`r nrow(relay)` episodes** since 2014.  

In `r year(now())-1`, there were **`r lastyear`** episodes published, and based on the average release frequencies, there will probably be **`r projection`** episodes in `r year(now())`. We're currently about **`r progress`%** of the way there at **`r thisyear`** episodes.

## Shows per Year

```{r show_peryear}
relay %>%
  group_by(podcast, year) %>%
  tally %>%
  ggplot(aes(x = as.factor(year), weight = n, fill = podcast)) +
  geom_bar() +
  scale_y_continuous(breaks = seq(0, 1000, 100),
                     minor_breaks = seq(0, 1000, 25)) +
  scale_fill_viridis(discrete = T) +
  labs(x = "Year", y = "# of Episodes", fill = "Show",
       title = expression(paste(italic("Relay.fm "), "Episodes per Year"))) +
  theme_background +
  theme_breaks_y +
  theme(legend.key.size = unit(.5, "cm"))

```

## Shows per Week

```{r shows_perweek}
relay %>%
  mutate(week = week(date)) %>%
  filter(year >= 2014) %>%
  group_by(year, week) %>%
  tally %>%
  {
  ggplot(data = ., aes(x = week, y = n)) +
  geom_point() +
  geom_smooth(data = filter(., year != 2016),
              method = lm, se = F, color = "red") +
  scale_y_continuous(breaks = seq(0, 100, 5),
                     minor_breaks = seq(0, 100, 1)) +
  scale_x_continuous(breaks = seq(0, 55, 16)) +
  facet_grid(.~year) +
  theme(strip.background = template_background,
        strip.text       = element_text(size = rel(1.2))) +
  labs(title = expression(paste(italic("Relay.fm "), "Weekly Episode Output")),
       x = "Week of Year", y = "Episodes Published") +
  theme_background +
  theme_breaks_y
  }
```

# Runtimes

## All Shows

```{r runtime_allshows, fig.height=8, fig.width=11}
relay %>%
  filter(podcast != "B-Sides") %>%
  {
    ggplot(., aes(x = date, y = duration)) +
      geom_point() +
     # geom_label_repel(data = filter(., duration > 160),
    #                   aes(label = title)) +
      expand_limits(y = 0) +
      #geom_smooth(method = loess, se = T) +
      scale_x_datetime(breaks = date_breaks("6 months"), minor_breaks = date_breaks("3 month"),
                       date_labels = "%b %Y") +
      scale_y_continuous(breaks = seq(0, 300, 30),
                         minor_breaks = seq(0, 300, 15)) +
      facet_wrap(~podcast, ncol = 7) +
      labs(title = expression(paste(italic("Relay.fm "), "Episode Durations")),
           x = "Date Published", y = "Duration (mins)") +
      theme_background +
      theme_breaks_y +
      theme(axis.text.x = element_text(angle = 45, vjust = .5))
  }
```

## Average by Show

### Boxplots 

```{r runtime_avg_pershow}
relay %>%
  #filter(podcast != "B-Sides") %>%
  group_by(podcast) %>%
  mutate(dur_mean = mean(duration)) %>%
         {
           ggplot(., aes(x = reorder(podcast, dur_mean), y = duration)) +
             geom_boxplot() +
             stat_summary(fun.y = "mean", geom = "point", size = 2, color = "red") +
             coord_flip() +
             scale_y_continuous(breaks = seq(0, 300, 30),
                                minor_breaks = seq(0, 300, 15)) +
             labs(title = expression(paste(italic("Relay.fm "), "Episode Duration — Boxplot + Mean (red)")),
                  x = "", y = "Duration (mins)") +
             theme_background +
             theme_breaks_x
         }

```

### 95% CI

```{r runtime_ci_pershow}
relay %>%
  #filter(podcast != "B-Sides") %>%
  group_by(podcast) %>%
  mutate(dur_mean = mean(duration)) %>%
  {
    ggplot(., aes(x = reorder(podcast, dur_mean), y = duration)) +
      stat_summary(fun.data = "mean_ci_t", geom = "errorbar") +
      stat_summary(fun.y = "mean", geom = "point", size = 2, color = "red") +
      coord_flip() +
      expand_limits(y = 0) +
      scale_y_continuous(breaks = seq(0, 300, 30),
                         minor_breaks = seq(0, 300, 15)) +
      labs(title = expression(paste(italic("Relay.fm "), "Episode Duration — 95% CI + Mean (red)")),
           x = "", y = "Duration (mins)") +
      theme_background +
      theme_breaks_x
  }
```

