---
title: "The Incomparable Podcast — In Numbers"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output:
  rmdformats::readthedown:
    highlight: kate
    self_contained: false
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
library(knitr)
library(rmdformats)
library(readr)
library(ggplot2)
library(magrittr)
library(dplyr)
library(lubridate)
library(tidyr)
library(DT)
library(viridis)
library(stringr)
library(ggrepel)

## Global options
options(max.print = "75")
opts_chunk$set(echo    = FALSE,
	             cache   = FALSE,
               prompt  = FALSE,
               tidy    = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE
             # dev = "svglite",
             # fig.ext = ".svg"
             )
opts_knit$set(width = 90)

incomparable      <- readRDS(file.path(data_dir, "incomparable_master.rds")) %>% 
                     filter(podcast == "The Incomparable")
incomparable_wide <- readRDS(file.path(data_dir, "incomparable_master_wide.rds")) %>% 
                     filter(podcast == "The Incomparable")

#### Plot presets ####
template_background <- element_rect(fill = "#fcfcfc", color = "#fcfcfc")

theme_background <- 
  theme(panel.background  = template_background,
        plot.background   = template_background,
        legend.background = template_background,
        strip.background  = template_background)

theme_breaks_x <-
  theme(panel.grid.major.x = element_line(size = .1, color = "black"),
        panel.grid.minor.x = element_line(size = .1, color = "black", linetype = "dotted"))
  
theme_breaks_y <-   
  theme(panel.grid.major.y = element_line(size = .1, color = "black"),
        panel.grid.minor.y = element_line(size = .1, color = "black", linetype = "dotted"))

duration_mins <- "Duration (mins)"
```

Note: This is a work in progress, and thise document is only a preview.  
I have **a lot** in mind for this project, but I *really really should be studying* right now.

# Introduction

Well, [Jason Snell tweeted](https://twitter.com/jsnell/status/700864025949655040) a graph of The Incomparable runtimes.  
As a big fan of the podcast and an aspiring nerd, [I asked for the data, obviously](https://twitter.com/Jemus42/status/700864609083850753).  
I was happy to [receive his .numbers file](https://twitter.com/jsnell/status/700864809537970176), but unfortunately [it only contained two variables](https://twitter.com/Jemus42/status/700870531697004544) - the two needed for the plot.  
Jason replied [he could get more metadata if I liked](https://twitter.com/jsnell/status/700870702367318017) and since I **really really would like** that, I rushed to set up [this repository](https://github.com/jemus42/theincompaRable) and put on my data-pants.  
A short time after that, [Jason delivered magnificiently](https://twitter.com/jsnell/status/700882298795765761).  
And now my analysis begins.

# Episodes Counts

## Episodes per Month / Year

```{r episodes_monthyear}
incomparable_wide %>%
  mutate(month = factor(month, levels = rev(levels(month)))) %>%
  ggplot(aes(x = month)) +
  geom_bar() +
  facet_grid(.~year) +
  coord_flip() +
  labs(y = "# of Episodes", x = "") +
  theme_background +
  theme_breaks_x
```

## Average Episode Count per Month

```{r episodes_month}
incomparable_wide %>%
  group_by(year, month) %>%
  tally() %>%
  group_by(month) %>%
  summarize(mean = mean(n)) %>%
  ggplot(aes(x = month, weight = mean)) +
  geom_bar() +
  labs(y = "# of Episodes", x = "") +
  theme_background +
  theme_breaks_y +
  theme(axis.text.x = element_text(angle = 45, vjust = .5))
```

## Episodes per Year

```{r episodes_year}
incomparable_wide %>%
  ggplot(aes(x = year)) +
  geom_bar() +
  labs(y = "# of Episodes", x = "") +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  theme_background +
  theme_breaks_y +
  theme(axis.text.x = element_text(angle = 45, vjust = .5))
```

# Runtime

## Histogram of All Episode Runtimes

```{r runtime_hist}
ggplot(data = incomparable_wide, aes(x = duration)) +
  geom_histogram(aes(fill = ..count..), binwidth = 5, color = "black") +
  scale_x_continuous(breaks = seq(0, max(incomparable$duration), 25)) +
  scale_fill_viridis(option = "magma") +
  labs(title = "The Incomparable Podcast\nShow Duration",
       x = duration_mins, y = "Count", fill = "Count") +
  theme_background +
  theme_breaks_y
```

## Scatterplot of All Episodes

The episode numbers in this are slightly off, due to [The Summer Superhero Spectacular](http://dump.jemu.name/nuwgL.png), which foiled my plans of representing the episode numbers numerically. I therefore numbered the episodes chronologically, so for example, episode number 258 is the 258th episode aired, but relative to the show's numbering, it's still part of 255.

```{r runtime_scatter}
cat <- incomparable_wide %>% group_by(category) %>% tally() %>% arrange(desc(n)) %>% extract2("category")
cat_colors <- RColorBrewer::brewer.pal(length(cat), "Set1")

incomparable_wide %>%
  arrange(date) %>%
  mutate(number_total = 1:nrow(.)) %>%
  plot_ly(data = ., x = number_total, y = duration, 
          mode = "markers", color = category, marker = list(size = 8), 
          colors = cat_colors,
          text = paste0("<b>", title, "</b>: ", number, 
                        "<br /><b>Segment:</b>", segment, 
                        "<br /><b>Topic:</b>", topic, 
                        "<br /><b>Category:</b>", category, 
                        "<br /><b>Published</b>: ", date,
                        "<br /><b>Duration</b>: ", round(duration, 2), " minutes",
                        "<br /><b>Host</b>: ", host, "<br /><b>Guests</b>:<br />", 
                        str_replace_all(guest, ", ", "<br />")),
          hoverinfo = "text") %>%
  layout(xaxis = list(title = "Total Episode #"), yaxis = list(title = "Duration (mins)",
                                                               rangemode = "tozero"),
         paper_bgcolor = "#fcfcfc", plot_bgcolor = "#fcfcfc")
```

## Runtime by Host

```{r runtime_by_host}
hosts <- incomparable_wide %>% group_by(host) %>% tally() %>% arrange(desc(n)) %>% extract2("host")
host_colors <- RColorBrewer::brewer.pal(length(hosts), "Set1")

incomparable_wide %>%
  mutate(host = factor(host, levels = rev(hosts), ordered = T)) %>%
  ggplot(data = ., aes(x = host, y = duration, fill = host)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Host", y = duration_mins) +
  scale_fill_manual(values = host_colors, guide = F) +
  theme_background +
  theme_breaks_x
```

## Runtime over Time

### Over Years

```{r runtime_years}
ggplot(data = incomparable_wide, aes(x = year, y = duration)) +
  geom_boxplot() +
  labs(x = "", y = duration_mins) +
  theme_background +
  theme_breaks_y
```

### Over Years/Months

```{r runtime_yearmonth, fig.height=8}
incomparable_wide %>%
  mutate(month = as.numeric(month)) %>%
  group_by(year, month) %>%
  summarize(duration = mean(duration)) %>%
  ggplot(aes(x = month, y = duration)) +
  geom_point() +
  geom_smooth(method = lm, se = F, color = "red") +
  scale_x_continuous(breaks = seq(0, 12, 6),
                   minor_breaks = seq(0, 12, 1)) +
  scale_y_continuous(breaks = seq(0, 200, 15),
                     minor_breaks = seq(0, 200, 5)) +
  facet_grid(.~year) +
  labs(title = "The Incomparable Podcast\nAverage Duration per Month",
       y = duration_mins, x = "") +
  theme_background +
  theme_breaks_x +
  theme_breaks_y +
  theme(strip.text = element_text(size = rel(1.2)))
```

# Topics / Categories

```{r categories}
incomparable_wide %>%
  group_by(category) %>%
  tally %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = reorder(category, n), weight = n)) +
  geom_bar() +
  coord_flip() +
  labs(title = "The Incomparable Podcast\nBy Categories",
       x = "Category", y = "# of Episodes") +
  theme_background +
  theme_breaks_x
```

# Guests

```{r guests}
incomparable %>%
  filter(role == "guest") %>%
  group_by(person) %>%
  tally %>%
  arrange(desc(n)) %>%
  filter(n > 2) %>%
  ggplot(aes(x = reorder(person, n), weight = n)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 1000, 20),
                     minor_breaks = seq(0, 1000, 10)) +
  labs(title = "The Incomparable Podcast\nGuest Appearances\n(3 Appearances Minumum)",
       x = "Guest", y = "# of Appearances") +
  theme_background +
  theme_breaks_x

incomparable %>%
  filter(role == "guest") %>%
  group_by(person) %>%
  summarize(n = n(), airtime_total = round(sum(duration), 2)) %>%
  arrange(desc(n)) %>%
  ungroup %>%
  mutate(perc_episodes = round((n/length(unique(incomparable$number))) * 100, 2),
         perc_guests   = round((n/sum(n)) * 100, 2)) %>%
  select(-airtime_total) %>%
  datatable(colnames = c("Guest", "Episodes", "Episode %", "% of Guests"))
```

# Acknowledgements

- Thanks to Jason for setting up the `stats.txt` files I parsed for the data.
- Thanks to [Juba](https://twitter.com/lapply) for the [RMarkdown template](https://github.com/juba/rmdformats)

# Related Documents

- [All shows](http://stats.jemu.name/theincomparable/results_incomparable_master.html)
- [Missing data](http://stats.jemu.name/theincomparable/missings.html)
- [All shows, raw data](http://stats.jemu.name/theincomparable/incomparable_raw.html)
